# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data

I started by loading the data from the file _activity.zip_ present in this folder.
This file has data that has recorded the activity of a person via a personal activity 
monitoring device during the month of October and November in 2012. The device collects data at five minute intervals throughout the day. The dataset has three columns: the number of steps taken during the 5-minute interval, the date, and the time of the interval (from 000 to 2355, resulting in 288 intervals per day).

```{r}
originalData <- read.csv(unz("activity.zip", "activity.csv"),header=T)
```

After loading the data, I cleaned the resulting data set from empty (NA) values.

```{r}
cleanData <- originalData[complete.cases(originalData$steps),]
```

## What is mean total number of steps taken per day?

One of the basic things to do with this kind of data is to see how many steps a
person takes during the day. First, let's make a histogram to see the distribution 
of the total number of steps in a day.

```{r}
dateSteps <- aggregate(cleanData$steps ~ cleanData$date, cleanData, FUN = sum)
colnames(dateSteps) <- c("date", "steps")
hist(dateSteps$steps, xlab = "Number of Steps Per Day", 
             main = "Histogram of Steps from Clean Data")
```

From the histogram we see that most often the person takes from 10,000 to 15,000 steps daily.

Next, lets calculate the mean (as integer):

```{r}
as.integer(mean(dateSteps$steps))
```

and the median:

```{r}
median(dateSteps$steps)
```


## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
